---
title: "Prediction using Supervised ML"
author: "Susmita Ghosh"
date: "15/12/2020"
output: html_document
---

### 1.Predict the percentage of a student based on the no. of study hours.

### 2.What will be predicted score if a student studies for 9.25 hrs/ day?

**Here we use Simple Linear regression to predict the percentage of an student based on the no.of study hours.**

**Percentage of a student is our study or dependent variable and no of study hours is independent variable.**

**Let's load the data first.**

```{r}
url<- "http://bit.ly/w-data"
data<- read.csv(url)
head(data)
```

**Data description and summary:**
```{r}
str(data)
summary(data)
```

**To visualize the data we do a Scatter plot between No of study hours and Percentage of a student.**

#### Scatter plot 
```{r}
plot(data,xlab="Hours",ylab="Scores",main= "Scatter plot of Hours vs Scores",col= "red")
```

**The scatter plot shows that there is a positive linear relationship between Percentage of a student and hours of study.**


**Let's look at the correaltion coefficent between these two variable:**
```{r}
cor(data$Hours,data$Scores)
```

**Now we are going to fit the linear model.**


#### The simple linear regression equation is given by: y=a+b*x;where,


*y= Dependent Variable*

*x= Independent Variable*

*a= Intercept*

*b= Slope*

#### Fit the linear model
```{r}
x=data$Hours
y=data$Scores
model<- lm(y~x,data)
summary(model)
```
### Add Regression line to the Scatter Plot
```{r}
x=data$Hours
y=data$Scores
model<- lm(y~x,data)
plot(data,xlab="Hours",ylab="Scores",main= "Scatter plot of Hours vs Scores",col= "red")
abline(model, col="blue")
```

### Predicted values based on the fitted model
```{r}
scores_predicted= model$fitted.values
scores_predicted
```

### Data set containing original scores and predicted scores
```{r}
new_data= data.frame(data$Hours,data$Scores,scores_predicted)
head(new_data)
```

### Plot predicted score vs original scores
```{r}
plot(new_data$data.Scores,new_data$scores_predicted)
```

### Scores of a student who studied 9.25hrs/day
```{r}
new_x=data.frame(x=9.25)
predict(model, new_x)
```

#### The Simple Linear Regression model for the given data set:y=2.4837+9.7758*x

**Summary of the model:**
*1.The percentage of a student is 2.4837 when there is study hours is zero.*

*2.By the unit change in the study hours the percentage of a student increases by 9.7758 unit.*

*3. By the Adj R squared value we see that 95.09% of the variance found in the study variable(scores) can be explained by predictor variable(study hours).*

